
---
title: "Scenario Report: COVID-19 Hospital Capacity"
date: "Generated on `r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    df_print: kable
    latex_engine: xelatex
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
fontsize: 11pt
geometry: margin=1in
params:
  t: NA
  young: NA
  medium: NA
  I_init: NA
  I_final: NA
  distribution: NA
  doublingtime: NA
  rampslope: NA
  M: NA
  L: NA
  L_occupied: NA 
  M_occupied: NA 
  Lfinal: NA 
  Lramp: NA 
  Mfinal: NA 
  Mramp: NA 
  avg_LOS_ICU: NA
  avg_LOS_Floor: NA
  p_death_ICU2: NA
  p_death_ICU3: NA
  p_death_floor2: NA
  p_death_floor3: NA
  doprotocols: NA
---


# Parameter Values 

```{r, echo=FALSE}
txt_params = text_parameters(t=params$t,
                     young=params$young,
                     medium=params$medium,
                     I_init=params$I_init,
                     I_final=params$I_final,
                     distribution=params$distribution,
                     doublingtime=params$doublingtime,
                     rampslope=params$rampslope,
                     M=params$M,
                     L=params$L,
                     L_occupied=params$L_occupied,
                     M_occupied=params$M_occupied,
                     Lfinal=params$Lfinal,
                     Lramp=params$Lramp,
                     Mfinal=params$Mfinal,
                     Mramp=params$Mramp,
                     avg_LOS_ICU=params$avg_LOS_ICU,
                     avg_LOS_Floor=params$avg_LOS_Floor,
                     p_death_ICU2=params$p_death_ICU2,
                     p_death_ICU3=params$p_death_ICU3,
                     p_death_floor2=params$p_death_floor2,
                     p_death_floor3=params$p_death_floor3)

rownames(txt_params) <- NULL

knitr::kable(txt_params)
```

# Plots 


```{r, echo=FALSE}
plots<-plot_hospital(t=params$t,
                     young=params$young,
                     medium=params$medium,
                     I_init=params$I_init,
                     I_final=params$I_final,
                     distribution=params$distribution,
                     doublingtime=params$doublingtime,
                     rampslope=params$rampslope,
                     M=params$M,
                     L=params$L,
                     L_occupied=params$L_occupied,
                     M_occupied=params$M_occupied,
                     Lfinal=params$Lfinal,
                     Lramp=params$Lramp,
                     Mfinal=params$Mfinal,
                     Mramp=params$Mramp,
                     avg_LOS_ICU=params$avg_LOS_ICU,
                     avg_LOS_Floor=params$avg_LOS_Floor,
                     p_death_ICU2=params$p_death_ICU2,
                     p_death_ICU3=params$p_death_ICU3,
                     p_death_floor2=params$p_death_floor2,
                     p_death_floor3=params$p_death_floor3,
                     doprotocols=params$doprotocols)

    plot(plots[[1]]) 
    plot(plots[[2]])
    plot(plots[[3]])
    plot(plots[[4]]) 
```

# Summary 


```{r, echo=FALSE}

txt <- text_hospital(t=params$t,
                     young=params$young,
                     medium=params$medium,
                     I_init=params$I_init,
                     I_final=params$I_final,
                     distribution=params$distribution,
                     doublingtime=params$doublingtime,
                     rampslope=params$rampslope,
                     M=params$M,
                     L=params$L,
                     L_occupied=params$L_occupied,
                     M_occupied=params$M_occupied,
                     Lfinal=params$Lfinal,
                     Lramp=params$Lramp,
                     Mfinal=params$Mfinal,
                     Mramp=params$Mramp,
                     avg_LOS_ICU=params$avg_LOS_ICU,
                     avg_LOS_Floor=params$avg_LOS_Floor,
                     p_death_ICU2=params$p_death_ICU2,
                     p_death_ICU3=params$p_death_ICU3,
                     p_death_floor2=params$p_death_floor2,
                     p_death_floor3=params$p_death_floor3,
                     doprotocols=params$doprotocols)

    knitr::kable(txt)
    
```




# About the application

This app implements a model for utilization of ICU beds, floor beds, and patient deaths due to COVID-19.  The model was developed by the COVID-19 Statistics,
Policy modeling and Epidemiology Collective (C-SPEC).  The app was written by [Soheil Eshghi](http://www.soheileshghi.com/), [Margret Erlendsdottir] (https://medicine.yale.edu/profile/margret_erlendsdottir/), 
[Maile Thayer Phillips](https://medicine.yale.edu/profile/maile_phillips/), [Suzan Iloglu](https://medicine.yale.edu/profile/suzan_iloglu/), [Christian Testa](https://ctesta.com) 
and [Forrest W. Crawford](http://www.crawfordlab.io) using the [R](http://www.r-project.org) [shiny](http://shiny.rstudio.com/) framework. 

We are especially grateful to [Gregg Gonsalves](https://medicine.yale.edu/profile/gregg_gonsalves/), [David Paltiel] (https://medicine.yale.edu/profile/david_paltiel/),
Hanna Ehrlich, Raphael Sherak,  Melanie Chitwood, Thomas Thornhill, [Nicole Swartwood](https://prevention-policy-modeling-lab.sph.harvard.edu/nicole-swartwood/), 
and Stephanie Perniciaro for advice and comments.  

Direct queries to <forrest.crawford@yale.edu>.

Source code at <https://github.com/fcrawford/covid19_icu>. 

Report issues to the [Github issues page](https://github.com/fcrawford/covid19_icu/issues).


